Stack Safety is a Security Property

### 2021-04-16 tex/main.tex

We are finally ready for our definition of stack safety. We begin
by describing how we model knowledge about the program structure,
then dive into the formal definitions of local state encapsulation and
well-bracketed control flow, which together constitute stack safety\BCP{need
  to put back WBCF!}.

@@

Naturally, testing also revealed a number of errors in our
implementation of the enforcement mechanism (the original was written in C++
and targeted ARM machine code
%\bcp{right?}\leo{yeah}
; we re-implemented it in Coq targeting RISC-V).  These errors ranged
from trivial typos to ones that required an intriguingly complex setup
to appear.  The most interesting bug (included in the table as row
{\em HEADER\_NO\_INIT}), in our first try the blessed call
sequence/policy combination did not initialize all locations for the
newly allocated stack frame correctly, but left some of them as
$\tagNoDepth$. This allowed for a potential integrity violation, but
only if a rather complicated sequence of events occured: in
particular, the smallest counterexample requires calling a function,
writing in the uninitialized location (which is always fine), calling
another function (to seal what was written for integrity purposes),
and then attempt to write in the same location again from the new
callee, which is only allowed because the enforcement still thinks
the location is unused, but violates the integrity of the caller's data.

\section{Stack Safety for Lazy Enforcement}
\label{sec:lazy}

>>>>

We are finally ready for our definition of stack safety. We begin
by describing how we model knowledge about the program structure,
then dive into the formal definitions of local state encapsulation\apt{we don't want
  to call it that here, do we?} and
well-bracketed control flow, which together constitute stack safety\BCP{need
  to put back WBCF!}.

@@

Naturally, testing also revealed a number of errors in our
implementation of the enforcement mechanism (the original was written in C++
and targeted ARM machine code
%\bcp{right?}\leo{yeah}
; we re-implemented it in Coq targeting RISC-V).  These errors ranged
from trivial typos to ones that required an intriguingly complex setup
to appear.  The most interesting bug (included in the table as row
{\em HEADER\_NO\_INIT}) was that, on our first try, the blessed call
sequence %/policy combination\apt{??}
did not initialize all locations for the
newly allocated stack frame correctly, but left some of them as
$\tagNoDepth$. This allowed for a potential integrity violation, but
only if a rather complicated sequence of events occured. 
The smallest counterexample requires calling a function {\tt f},
which writes into an uninitialized location $l$ (which is always fine), and then
calls a further function {\tt g} (which should have the effect of sealing $l$
for integrity purposes). Then {\tt g} attempts to write to $l$; 
this is allowed because the enforcement mechanism still has 
$l$ tagged as $\tagNoDepth$, but violates the integrity property on {\tt f}'s data.
\section{Stack Safety for Lazy Enforcement}
\label{sec:lazy}
